Lightweight Ruby Framework for Improving Embedded Software Efficiency

### 2016-06-10 CPSNA2016/paper.tex
update CPSNA2016

\section{Introduction}
Cyber Physical Systems (CPS) are the important keyword for enriching our lives.
Embedded systems e.g., Internet of Things applications, are applied to the CPS and expected to demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.
% mruby on TECS supports to effectively run mruby script language on embedded systems.
% mruby on TECS also makes execution time 100 times faster than that of mruby.
%This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
Execution times of mruby on TECS are 100 times faster than those of mruby, which are the same as those of C language.
Moreover, Ruby is often utilized in network programming, therefore the framework can be applicable for the software involved network such as CPS applications.

@@

\section{System Model}
\label{sec:System Model}
The proposed framework is an extended framework of mruby on TECS, and utilizes mruby and TECS.
These basic technologies are described in appendix of this paper.

@@

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality, i.e., the Bluetooth loader.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the completed software production should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once. 
An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} has supported a load of object files.
The proposed loader newly supports a load of bytecodes.

@@

\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time of Singletask, Proposed Multitask, Existing Multitask, and Co-routine}
Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
The {\it delay} function and co-routine method run on a RiteVM, which causes the slow-down compared to the proposed multitasking.
The scheduler runs as the periodic handler of RTOS.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitask and co-routine.
% Therefore, the scheduler enables developers multitask as the more efficient approach than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
% It takes approximately 3 $\mu$sec on average to switch tasks once.

@@

\clearpage
\appendices
\section{mruby}
mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[h]
    \centering
    \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
    \vspace{-2mm}
    \caption{mruby/RiteVM mechanism}
    \vspace{-2mm}
    \label{fig:mruby}
\end{figure}

\section{TECS}
TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
    \vspace{-2mm}
    \caption{Component Diagram}
    \vspace{-5mm}
    \label{fig:component}
\end{figure}

@@

\begin{figure}[H]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Build Description}
    \vspace{-2mm}
\label{build}
\end{figure}

@@

\section{mruby on TECS}
\subsection{System Model}
The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
% In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
    \vspace{-2mm}
\caption{System model of existing mruby on TECS}
    \vspace{-2mm}
\label{fig:mrubyontecs}
\end{figure}

\subsection{mruby-TECS Bridge}
There is a significant difference between the execution times of mruby and C language codes.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
Thus, it is difficult to use mruby exclusively.

Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
% On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.

Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
    \vspace{-2mm}
\caption{mruby-TECS bridge}
    \vspace{-2mm}
\label{fig:mruby_TECS_bridge}
\end{figure}

The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.

The generated mruby-TECS bridge supports registration of classes and methods for mruby.
Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.

\end{document}

>>>>

\section{Introduction}
Cyber Physical Systems (CPS) are the important keyword for enriching our lives.
Embedded systems are applied to the CPS and expected to demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}.
% mruby on TECS supports to effectively run mruby script language on embedded systems.
% mruby on TECS also makes execution time 100 times faster than that of mruby.
%This paper proposes two additional features of mruby on TECS, Bluetooth loader for mruby bytecode and RiteVM scheduler.
Execution times of mruby on TECS are 100 times faster than those of mruby, which are the same as those of C language.
Moreover, Ruby is often utilized in network programming, therefore mruby on TECS can be applicable for the software involved network such as CPS applications.

@@

\section{System Model}
\label{sec:System Model}
The proposed framework is an extended framework of mruby on TECS\footnote{mruby on TECS is explained in detail in \cite{par:mrubyonTECS}}, and utilizes mruby and TECS.
mruby and TECS are described in Appendixes \ref{apn:mruby} and \ref{apn:TECS}.

@@

\subsection{Bluetooth Loader for mruby Bytecode}
\label{sec:Bluetooth loader for mruby bytecode}
This section describes the proposed additional functionality, i.e., the Bluetooth loader.\footnote{
The Bluetooth loader is intended to improve development efficiency; therefore, software developers should use it during the development phase.
Note that the bytecode after the development phase should be compiled and linked on the storage/ROM device beforehand.
}
In the current system, the platform including mruby bytecodes is saved on a storage/ROM device.
Developers must rewrite the storage/ROM device every time the programs are modified.
In addition, the RTOS on the target device needs to be restarted.
The repetition hinders development efficiency.
The Bluetooth loader for mruby bytecode decreases developer burden because developers only have to connect the storage/ROM device and start the RTOS once. 
An existing Bluetooth-based loader such as TOPPERS/EV3RT \cite{par:EV3} has supported a load of object files.
The proposed loader newly supports a load for bytecodes of scripting languages.

@@

\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_s_c_m.eps}
    \vspace{-3mm}
\caption{Comparison of application execution time}
    \vspace{-3mm}
\label{fig:comparison_s_c_m}
\end{figure}
\begin{figure}[t]
    \centering
    \includegraphics[height=3.0cm,width=7.0cm,clip]{figure/comparison_msec.eps}
    \vspace{-3mm}
\caption{Comparison of overhead for each cyclic period of RiteVM scheduler}
    \vspace{-3mm}
\label{fig:comparison_msec}
\end{figure}
\subsubsection{Execution Time of Singletask, Proposed Multitask, Existing Multitask, and Co-routine}
Figure \ref{fig:comparison_s_c_m} shows that the proposed design is superior to multitask using delay method and co-routine in terms of execution time.
The {\it delay} and co-routine methods run on a RiteVM, which causes the slow-down compared to the proposed multitasking.
The scheduler runs as the periodic handler of RTOS.
Moreover, developers can utilize the scheduler practically because the RiteVM scheduler overhead is approximately 5\%.
The scheduler interrupts and switches tasks, which causes this overhead.
Although the overhead is larger as the number of RiteVMs increases, it also spread the difference between multitask and co-routine.
Therefore, the scheduler is the more efficient approach for multitasking than the existing multitasking and co-routine.
Here, the periodic time of the scheduler is 1 msec.
% It takes approximately 3 $\mu$sec on average to switch tasks once.

@@

\clearpage
\appendices
\section{mruby}
\label{apn:mruby}
mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
Ruby is an object-oriented scripting language with classes and methods, exceptions, and garbage collection functions.
It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[b]
    \centering
    \includegraphics[height=5.0cm,width=8.6cm,clip]{figure/mruby.eps}
    \vspace{-3mm}
    \caption{mruby/RiteVM mechanism}
    \vspace{-3mm}
    \label{fig:mruby}
\end{figure}

\section{TECS}
\label{apn:TECS}
TECS is a component system suitable for embedded systems.
TECS can increase productivity and reduce development costs due to improved reusability of software components.
TECS also provides component diagrams, which help developers visualize the overall structure of a system.

@@

\begin{figure}[b]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
    \vspace{-2mm}
    \caption{Component Diagram}
    \vspace{-5mm}
    \label{fig:component}
\end{figure}

@@

@@

\begin{figure}[H]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
    \vspace{-2mm}
\caption{Build Description}
    \vspace{-2mm}
\label{build}
\end{figure}
% \section{mruby on TECS}
% \subsection{System Model}
% The present mruby on TECS system model is shown in Figure \ref{fig:mrubyontecs}.
% Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
% TECS components support various embedded drivers such as motor and sensor drivers.
%
% An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
% The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.
% % In this paper, TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} with memory protection.
% mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs.
%
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
%     \vspace{-2mm}
% \caption{System model of existing mruby on TECS}
%     \vspace{-2mm}
% \label{fig:mrubyontecs}
% \end{figure}
%
% \subsection{mruby-TECS Bridge}
% There is a significant difference between the execution times of mruby and C language codes.
% According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
% Thus, it is difficult to use mruby exclusively.
%
% Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
% However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.
% % On the other hand, it is necessary to implement parts of applications in C language in order to manipulate actuators and sensors, and also make critical sections of the code run quickly.
%
% Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
% The left side of BridgeMotor belongs to the mruby program.
% The right side of BridgeMotor belongs to TECS component.
% \begin{figure}[t]
%     \centering
%     \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
%     \vspace{-2mm}
% \caption{mruby-TECS bridge}
%     \vspace{-2mm}
% \label{fig:mruby_TECS_bridge}
% \end{figure}
%
% The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.
%
% The generated mruby-TECS bridge supports registration of classes and methods for mruby.
% Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
% Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
%
\end{document}
